\section{Experimental Setup}
\label{sec:experiments}

\subsection{Models}

We evaluate six production models spanning all major frontier AI providers and leading open-weight alternatives:

\begin{itemize}[nosep,leftmargin=*]
  \item \textbf{GPT-4o} (OpenAI): frontier multimodal model accessed via the OpenAI API.
  \item \textbf{Claude Sonnet 4} (Anthropic): frontier model accessed via the Anthropic API.
  \item \textbf{Gemini 2.5 Pro} (Google): frontier model accessed via the Gemini API's OpenAI-compatible endpoint.
  \item \textbf{DeepSeek-V3} (DeepSeek): frontier model accessed via the DeepSeek API.
  \item \textbf{Llama-3.3-70B-Instruct} (Meta): open-weight model served via Together AI.
  \item \textbf{Qwen3-32B} (Alibaba): open-weight model served via Groq.
\end{itemize}

This selection covers the three leading safety-focused labs (Anthropic, Google, OpenAI) alongside frontier and open-weight alternatives with distinct training philosophies. All models are accessed with temperature $T=0.3$ and maximum output length of 2048 tokens. No few-shot examples are provided.

\subsection{Conditions}

Each model is evaluated under two conditions on all 24 public-safe items, yielding $6 \times 2 \times 24 = 288$ total responses across all labs and model families:

\begin{itemize}[nosep,leftmargin=*]
  \item \textbf{Pre-mitigation}: no system prompt. The model receives only the user prompt.
  \item \textbf{Post-mitigation}: a standardized safety system prompt instructs the model to prioritize evidence-grounded responses, acknowledge uncertainty, respect safety boundaries, and provide safe alternatives when refusing.
\end{itemize}

\subsection{Scoring Procedure}

Responses are scored using a systematic protocol aligned with the annotation handbook (\Cref{sec:rubric}):

\begin{enumerate}[nosep,leftmargin=*]
  \item Each response is evaluated against expected behavior tags defined in its item metadata.
  \item Domain-family-specific scoring criteria determine the relative weight of each metric.
  \item Pattern-based indicators (uncertainty markers, evidence citations, safe redirects, overconfidence markers) assign initial scores adjusted by mitigation condition.
  \item Error tags are assigned when responses exhibit specific failure modes.
\end{enumerate}

\subsection{LLM-as-Judge Validation}
\label{sec:llm_judge}

To validate scoring reliability, we employ an independent LLM-as-judge approach. Claude Sonnet 4 scores each response using the same rubric (metric definitions, scoring anchors, error tag vocabulary) provided in its system prompt. The judge receives the full item metadata and response text, and produces structured JSON output with five metric scores and error tags.

We compute inter-rater agreement between the pattern-based scorer and the LLM judge using Cohen's $\kappa$ (binarized at threshold 4), mean absolute divergence, and error-tag exact-match rate. This dual-scoring approach enables:
\begin{enumerate}[nosep,leftmargin=*]
  \item \textbf{Scoring validation}: verification that systematic pattern-based scoring aligns with independent semantic evaluation.
  \item \textbf{Failure mode identification}: cases where scorers disagree highlight items with ambiguous safety behavior.
  \item \textbf{Reproducibility}: the LLM-as-judge protocol can be replicated by other researchers using the same prompt.
\end{enumerate}

\subsection{Statistical Analysis}

All reported means include 95\% bootstrap confidence intervals (10,000 resamples). Mitigation effectiveness is tested using Wilcoxon signed-rank tests (paired by item, $n=24$). Cross-model differences are assessed using Friedman tests. Effect sizes are reported as Cohen's $d$ and rank-biserial correlation.

\subsection{Analysis Pipeline}

All scripts, configurations, and intermediate outputs are included in the release package for full reproducibility. The pipeline includes per-model audit summaries, cross-model comparison scorecards, domain-family breakdown analysis, and taxonomy coverage validation.
